A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-13 PPSN2016/paper.Rnw
Explaining correlation but maybe @mariosky or @fergunet have a better idea

\begin{table}[htbp]
  \caption{Minute-wise correlation for number of participating volunteers. \label{tab:correlation}}
\begin{center}
<<correlations, cache=FALSE,echo=FALSE>>=
#experiment.aggregates$Experiment <- c("base","graph1","graph2","reboot","cachereboot")
kable(ip.correlations)
@ %def correlations
\end{center}
\end{table}
%
We can check this impact by looking at the column that refers to
median time in Table \ref{tab:filtered} and its relation to the median
number of PUTs, which reflects the number of evaluations performed by
the clients. The two last rows have a low number of evaluations,
around 650, which is higher than the first two, probably due to the
lower volunteer supply, but better than the middle one; besides, the
amount is remarkably similar. But in the last case, it takes much less
time to find the solution {\em using the same number of
  evaluations}. All variables are difficult to control in this
environment, but it might be due to the fact that parallelism has
increased, there are more volunteers contributing at the same time. In
fact, as can be seen in the last column, the median number of
contributions per user is {\em much lower} in the last row, which
indicates that {\tt cachereboot} needs less contributions by users to
find the same solution. Besides, the last row shows that {\em all}
users actively contribute to the cache, while in the {\tt reboot}
strategy 30\% of users do not. This might be due to the fact that {\tt
  reboot} only does so when cache size is less than one. With very
fast clients there might be some clients that do not detect that
change and might, in fact continue with their former run, thus not
contributing to the common cache.

>>>>

\begin{table}[htbp]
  \caption{Minute-wise correlation for number of participating volunteers. \label{tab:correlation}}
\begin{center}
<<correlations, cache=FALSE,echo=FALSE>>=
ip.correlations$Experiment <- c("base","graph1","reboot","cachereboot")
kable(ip.correlations)
@ %def correlations
\end{center}
\end{table}
%
We can check this impact by looking at the column that refers to
median time in Table \ref{tab:filtered} and its relation to the median
number of PUTs, which reflects the number of evaluations performed by
the clients. The two last rows have a low number of evaluations,
around 650, which is higher than the first two, probably due to the
lower volunteer supply, but better than the middle one; besides, the
amount is remarkably similar. But in the last case, it takes much less
time to find the solution {\em using the same number of
  evaluations}. All variables are difficult to control in this
environment, but it might be due to the fact that parallelism has
increased, there are more volunteers contributing at the same time. In
fact, as can be seen in the last column, the median number of
contributions per user is {\em much lower} in the last row, which
indicates that {\tt cachereboot} needs less contributions by users to
find the same solution. Besides, the last row shows that {\em all}
users actively contribute to the cache, while in the {\tt reboot}
strategy 30\% of users do not. This might be due to the fact that {\tt
  reboot} only does so when cache size is less than one. With very
fast clients there might be some clients that do not detect that
change and might, in fact continue with their former run, thus not
contributing to the common cache.

In fact, as can be seen in Table \ref{tab:correlations}, which shows
the correlation between the number of IPs from one minute to the next,
the behavior of all experiments but the last one are similar, with a
very high correlation indicating that the number of volunteers does
not change from one minute to the next. However, there is a sharp drop
for the {\tt cachereboot} experiment, which indicates a bigger
dynamism, with individuals joining and leaving the experiment all the
time. This might be circumstancial, but it also reflects the fact
that the solution is found in less time and that users need less
contributions to find it personally.
